A holomorphic approach to membranes and fivebranes

### 2022-07-11 fivebranes/twisted.tex

\section{Twists in dimensions three, six, and eleven}

@@

By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a twisting supercharge.

Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
\begin{itemize}
\item 
The minimal twist. 
This twist leaves six real directions invariant and is preserved by the subgroup $SU(5)$ of the Lorentz group. 
\item 
The non-minimal twist. 
This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
\end{itemize}

@@

In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze twists of $M$ theory, starting with an $\Omega$-deformation of the nonminimal twist of eleven-dimensional supergravity. Using a type IIA description, the theory was shown to admit a description in terms of a holomorphic-topological gauge theory in five dimensions with a well-behaved quantization.

The five-dimensional theory is also a $\Z/2$-graded within the BV formalism and exists on any manifold of the form
\[
  S\times Y
\]

@@

The fields of the theory are given by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
\beqn
\cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
\eeq

The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket $\{-,-\}_{Y}$. This can be extended in a graded way to the entire Dolbeault complex; $\cL_{5d}$ is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.

@@

The equations of motion of $\cL_{5d}$ describe locally-constant families of deformations of the fixed holomorphic Poisson structure on $Y$.

@@

This theory notoriously does not admit a Lagrangian description. 
However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
We describe this Poisson bivector explicitly

In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{single} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]

>>>>

\section{Twists in dimensions eleven, six, and three}

@@

By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a nilpotent supercharge. Such backgrounds have the feature that the worldvolume theories of branes in their presence are twisted.

Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the dimension of the subspace of translations spanned by the image of $Q$.
\begin{itemize}
\item 
The minimal twist. 
This twist leaves six real directions invariant and is preserved by the subgroup $SU(5)$ of the Lorentz group. 
\item 
The non-minimal twist. 
This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
\end{itemize}

@@

\surya{ FINISH }

In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze holography for membranes and fivebranes in eleven dimensional supergravity, starting with an $\Omega$-deformation of the nonminimal twists.

The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.

The five-dimensional theory is $\Z$-graded within the BV formalism and exists on any manifold of the form
\[
  S\times Y
\]

@@

As a gauge theory, the fundamental field is a one-form. The space of complex-valued one-forms on $S\times Y$ decomposes into de Rham-Dolbeault forms as
\[
\oplus_{k+p+q=1}\Omega^{k}(S)\otimes \Omega^{p,q}(Y).
\]

and we continue to label elements of the homogeneous pieces as $(k;p,q)$ forms. The fields of ghost number zero are those one-forms with $p=0$. We will use the notation $\alpha^{k;q}$ with $k+q=1$ for the corresponding component of the one-form.

These fields are subject to the equations of motion

\beqn
0 = \dbar \alpha^{0;1} + \frac{1}{2}\{\alpha^{0;1}, \alpha^{0;1}\}_Y
0 = d\alpha^{0;1}+\dbar \alpha^{1;0}+ \{\alpha^{0;1}, \alpha^{1;0}\}_Y
\eeqn

where $\{-,-\}_{Y}$ denotes the holomorphic Poisson bracket on $Y$.

We may get a better feeling for these equations upon giving $\alpha^{{1;0}}$ a VEV such that $\dbar\alpha^{{1;0}}=0$. The secnod equation then reads

\beqn
0 = d\alpha^{0;1} + \{\alpha^{1;0}, \alpha^{0;1}\}
\eqn

The fields $\alpha^{{k;q}}$ have a gauge symmetry determined by a ghost $b \in \Omega^{0}(S\times Y)$. Explicitly, the corresponding infinitessimal gauge transformation is given by
\[
\alpha^{k;q}\mapsto \alpha^{k;q} + db+\dbar b + \{b, \alpha^{k;q}\}_{Y}
\].

In the BV formalism, the fields are described by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is

\beqn
\cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
\eeqn

The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a lie bracket on the entire Dolbeault complex; $\cL_{5d}$ is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.

@@

@@

This theory notoriously does not admit a Lagrangian description. 
However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
We describe this Poisson bivector explicitly
\surya{ FINISH }
In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{single} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]
